\documentclass{article}
\pagenumbering{arabic}

\begin{document}
\title{How to have fun in a club without your girlfriend/boyfriend}
\author{JOSE}
\maketitle
\section{intoduction}
\subsection{small intro}
Most people actually go out with their girlfriends/boyfriends maybe a bar or hangout because they think it is fun to be with people they share feelings with. To some it is fun, to some others its inconvenient because some people don’t like congested places. Some other people don’t go with people they date because they can get a little jealous if they tend to look at others, or even in fear of being abandoned for other people. So I think I have a way for people to have fun in clubs and hangouts without their boyfriends and girlfriends.
\section{items}
The first item on the list should a venue, the place should be convenient and nearer to avoid added transport costs. The second item should the group of people to accompany to the club/hangout considering the kind of people you are going with. If you want to have fun go with hyped up people who won’t let you down. Make sure you also go in the group of about 3 to 5 people so that you can have “sike”, ie energy and gas to dance and enjoy and fun during the night. The next item is the amount of money you have, make sure you have enough money for the night. For the ladies you are dependant if you want to have good and enough fun, because you may wait to detooth some men and they won’t accept or maybe everyday you detooth but when today is not your day, just make sure you carry enough cash. Cover the transport costs too because we have seen people walking home, hmm things are real.
\section{the donts}
You are the set for the bar with the above items. Make some rules for while in the bar like no whatsapping (using the whatsapp application) in your group for that time in the bar. Anyone who does that is fined to buy mobile data for everyone in that group for the next day. Also make sure that your phones are stolen because its common these days to steal phones in many hangout places, have jeans with long pockets , you don’t want  to get shocked because your night will be spoilt and it will be the end. The night can officially start. You can set off at 10 pm and arrive the hangout latest by 11pm and you can start the pare.
\section{the night}
You can get in get your table for table for the five of you and order your drinks. Most people prefer alcohol, some people want beverages, and use water to try to blow steam of height. When deejay starts doing what he does best then the drinking starts. The dance moves kick in and then the shouting helps you release stress. This is where there is an advantage of the group when people start getting drank and bar fights, the other friends are there to protect you such nasty things in the bar.
Make sure if you are drinking alcohol don’t down bottles very fast or you will get very fast and may not actually enjoy after all, so you drink because you have all the time in the world. Dance as much as you as you drink , it will feel very nice and fun. If alcohol gets done and you have more money buy more alcohol and more water because it helps. For some people it’s not a night if they haven’t gotten a rub dub(dancing with a girl body to body) , so they may start looking for them. Don’t make a mistake of attacking someone’s girlfriend, cause you will be beaten. Where possible get a person who appears free and looks like may accept otherwise stay on your plan, Drink, dance and have fun.

\end{document}